Structured Versus Decorated Cospans

### 2020-12-03 cospans.tex
changing order of composition

We thank Daniel Cicala, Brendan Fong, and Joe Moeller for helpful conversations.

@@

Finally, the (horizontal) composition functor $\odot$ maps two composable $F$-decorated cospans $\left(a\to m\leftarrow b,x\in F(m)\right)$ and $\left(b\to n\leftarrow c,y\in F(n)\right)$ to their pushout in $\A$ over their shared foot

@@

with decoration
$$x\odot y:= \one\cong\one \times \one \xrightarrow{x \times y} F(m) \times F(n) \xrightarrow{\phi_{m,n}} F(m+n) \xrightarrow{F(\psi)} F(m+_{b}n)$$

@@

their composite $\alpha \odot \beta$ is horizontal cospan composition in $\A$

@@

together with the decoration morphism $\tau_{\alpha \odot \beta} \colon F(h_1 +_g h_2)(x \odot y) \to (x' \odot y')$ given by the diagram:

@@

the isomorphism $(M_1\odot M_2)\odot M_3\cong M_1\odot (M_2\odot M_3)$ is the isomorphism of cospans 

@@

\node (E) at (5.5,0.5) {$(x_1 \odot x_2) \odot x_3 \in F((m_1+_{b} m_2)+_{c} m_3)$};
\node (F) at (5.5,-0.5) {$x_1 \odot (x_2 \odot x_3) \in F(m_1+_{b} (m_2 +_{c} m_3))$};

@@

together with an isomorphism $F(\kappa)((x_1 \odot x_2) \odot x_3) \cong (x_1 \odot (x_2 \odot x_3))$ between the decorations 

@@

\begin{thm} \label{thm:equiv}
Suppose $\A$ has finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\Rex$ as an ordinary pseudofunctor. Then the symmetric monoidal double categories $F\lCsp$ of decorated cospans and $_L\lCsp(\inta F)$ of structured cospans are isomorphic, where $L \maps \A \to \inta F$ is a left adjoint of the induced Grothendieck opfibration $U\maps \inta F \to \A$.
\end{thm}

@@

Building up to an isomorphism of the above described double categories, we now define a double functor
\begin{displaymath}
\lE=(\lE_0,\lE_1)\maps _L\lCsp(\inta F) \longrightarrow F\lCsp
\end{displaymath}
which on vertical categories acts as the identity $\lE_0 = \id_{\A}$. Given a horizontal 1-cell in $_L\lCsp(\inta F)$ as in \cref{eq:scsphor1cell}, $\lE_1$ maps it to the decorated cospan $i\maps a\to m\leftarrow b:o$ with decoration $x\in F(m)$,
whereas a 2-morphism of $L$-structured cospans as in \cref{eq:2morphismLCspintaF} is mapped to the underlying map of cospans in $\A$
\begin{displaymath}
\begin{tikzcd}
a\ar[r,"i"]\ar[d,"f"'] & m\ar[d,"k"] & b\ar[l,"o"']\ar[d,"g"] \\
a'\ar[r,"i'"']& m' & b'\ar[l,"o'"]
\end{tikzcd}
\end{displaymath}
in $\A$ along with the map $\tau\maps Fk(x)\to x'$ in $F(m')$ coming from the middle arrow above, namely an $F$-decorated cospan 2-morphism. 
With these definitions, $\lE$ is indeed a double functor as in \cref{def:doublefun}: both $\lE_0$ and $\lE_1$ are functors that appropriately commute with sources and targets, and there exist globular 2-isomorphisms $\lE(M) \odot \lE(N) \simrightarrow\lE(M \odot N)$, $U_{\lE m} \simrightarrow\lE(U_m)$
for any pair of composable horizontal 1-cells $M=\cspn{(a,\bot_a)}{(m,x)}{(b,\bot_b)}{}{}$ and $N=\cspn{(b,\bot_b)}{(n,y)}{(c,\bot_c)}{}{}$ and any object $m$ of $_L\lCsp(\inta F)$. Explicitly, $\mathbb{E}(M)\odot \mathbb{E}(N)$ is given as in \cref{eq:dcospanscomposition} via the pushout cospan and decoration
\begin{equation}\label{eq:1}
 \begin{tikzcd}
  & m+_bn & \\
  a\ar[ur] && b,\ar[ul]
 \end{tikzcd}\qquad
  \one\xrightarrow{x\times y}F(m)\times F(n)\xrightarrow{\phi_{m,n}}F(m+n)\xrightarrow{F(\psi)}F(m+_bn)
\end{equation}
whereas first composing $M$ and $N$ in $_L\lCsp(\inta F)$ using pushouts in $\inta F$ as in \cref{eq:globalpushout} produces 
\begin{displaymath}
 \begin{tikzcd}[column sep={.7in,between origins}]
 && (m+_b n,F(u_m)x+_{(\bot_{m+_bn})}F(u_n)y) && \\
 & (m,x) \ar[ur] && (n,y)\ar[ul] \\
 (a,\bot_a)\ar[ur] && (b,\bot_b)\ar[ur]\ar[ul] && (c,\bot_c)\ar[ul]
 \end{tikzcd}
\end{displaymath}
where $u$ are the canonical maps into the pushout.
Under $\lE$ this is mapped to the underlying $\A$-cospan $\cspn{a}{m+_bn}{b}{}{}$ with decoration $F(u_m)x+F(u_n)y$, since a pushout over an initial object is really a coproduct. That decoration is isomorphic to that of \cref{eq:1} due to the following diagram 
\begin{equation}\label{eq:isomorphismdiag}
 \begin{tikzcd}
F(m)\times F(n)\ar[rr,"\phi"]\ar[d,"F(u_m)\times F(u_n)"']\ar[dr,phantom,"\cong"] && F(m+n)\ar[d,"F(\psi)"]\ar[d,bend right=50, phantom,"\cong"']\ar[dl,"F(u_m+u_n)"description] \\
F(m+_bn)\times F(m+_bn)\ar[r,"\phi"'] & F\left((m+_bn)+(m+_bn)\right)\ar[r,"F(\nabla)"'] & F(m+_bn)
 \end{tikzcd}
\end{equation}
where the bottom composite is the fibrewise coproduct in $F(m+_bn)$ as in \cref{eq:explicitstructure1}. The left-hand side isomorphism is due to pseudonaturality of $\phi$ whereas the right-hand side isomorphism follows from universal properties and pseudofunctoriality of $F$.
Regarding identities, the identity horizontal 1-cell $U_m$ in $_L\lCsp(\inta F)$ is $\cspn{(m,\bot_m)}{(m,\bot_m)}{(m,\bot_m)}{}{}$ with $1_m$ as the $A$-component and isomorphisms between initial objects in the fibres. Thus $\lE(U_m)$ is the identity cospan in $A$ together with the `initial decoration' $\bot_m\in F(m)$, and so is $U_{\mathbb{E}(m)}$ as in \cref{eq:UFCsp}. %Do we want to check that E is a double functor one last time?

@@

%\begin{defn}
%Let $\lD$ be a pseudo double category. Then the $\textbf{horizontal bicategory}$ of $\lD$, which we denote as $H(\lD)$, is the bicategory consisting of objects of $\lD$, morphisms that are horizontal 1-cells of $\lD$ and 2-morphisms that are globular 2-morphisms of $\lD$.
%\end{defn}
\begin{defn}\label{def:doublefun}
Given double categories $\lA$ and $\lX$, a \define{double functor} $\lF \colon\lA \to \lX$ consists of:
\begin{itemize}
\item{functors $\lF_0 \colon \lA_0 \to \lX_0$ and $\lF_1 \colon \lA_1 \to \lX_1$ such that $S \lF_1 = \lF_0 S$ and $T \lF_1 = \lF_0 T$, and}
\item{for every composable pair of horizontal 1-cells $M$ and $N$ in $\lA$, a natural transformation $\phi_{M,N} \colon \lF(M) \odot \lF(N) \to \lF(M \odot N)$ called the \define{composite comparison} and for every object $a$ in $\lA$, a natural transformation $\phi_a \colon U_{\lF_0(a)} \to \lF_1(U_a)$ called the \define{unit comparison}. The components of each of these natural transformations are globular isomorphisms which satisfy coherence axioms analogous to those of a monoidal functor.}
\end{itemize}
\end{defn}

@@

\begin{defn}
\label{defn:monoidal_double_category}
A \define{monoidal double category} is a pseudomonoid in $\Dbl$. 
\end{defn} 
\noindent
Explicitly, a monoidal double category is a double category $\lD$ with:
\begin{itemize}
\item monoidal structures on both $\lD_0$ and $\lD_1$, each with tensor product denoted $\otimes$, associator $a$, left unitor $\ell$ and right unitor $r$, such that if $I$ is the unit object of $\lD_0$ then $U_I$ is\footnote{\chris In reality, just isomorphic is OK!} the unit of $\lD_1$, and such that the source and target functors $S,T \maps \lD_1 \to \lD_0$ are strict monoidal, 
\item the structure of a double functor on $\otimes$:
that is, invertible globular 2-morphisms
\[ \chi \maps (M_1\otimes N_1)\odot (M_2\otimes N_2) \xrightarrow{\sim}
(M_1\odot M_2)\otimes (N_1\odot N_2)\]
\[ \mu \maps U_{A\otimes B} \xrightarrow{\sim} U_A \otimes U_B\]
obeying a list of equations that can be found after \cite[Definition 2.10]{HS} and also \cite[Definition A.5]{BC}.
\end{itemize}

\begin{defn}
\label{defn:symmetric_monoidal_double_category}
A \define{symmetric monoidal double category} is a symmetric pseudomonoid in $\Dbl$. 
\end{defn}
\noindent
Explicitly, a symmetric monoidal double category is a monoidal double category $\lD$ such that:
\begin{itemize}
		\item $\lD_0$ and $\lD_1$ are symmetric monoidal categories, with braidings both denoted $\beta$.
		\item The functors $S$ and $T$ are symmetric strict monoidal functors.
		\item The following diagrams commute, expressing that the braiding is a transformation of double categories:
		\begin{equation}
		\begin{tikzpicture}\label{eq:braidingaxiom}
			\node (A) at (0,1.5) {\footnotesize{$(M_1 \odot M_2) \otimes (N_1 \odot N_2)$}};
			\node (A') at (0,0) {\footnotesize{$(M_1\otimes N_1) \odot (M_2\otimes N_2)$}};
			\node (B) at (5,1.5) {\footnotesize{$(N_1\odot N_2) \otimes (M_1 \odot M_2)$}};
			\node (B') at (5,0) {\footnotesize{$(N_1 \otimes M_1) \odot (N_2 \otimes M_2)$}};
			%
			\path[->,font=\scriptsize]
				(A) edge node[left]{$\chi$} (A')
				(A) edge node[above]{$\beta$} (B)
				(B) edge node[right]{$\chi$} (B')
				(A') edge node[above]{$\beta \odot \beta$} (B');
		\end{tikzpicture}
		%
		\quad
		%
		\begin{tikzpicture}
			\node (A) at (0,1.5) {\footnotesize{$U_A \otimes U_B$}};
			\node (A') at (0,0) {\footnotesize{$U_B\otimes U_A$}};
			\node (B) at (2,1.5) {\footnotesize{$U_{A\otimes B} $}};
			\node (B') at (2,0) {\footnotesize{$U_{B\otimes A}$}};
			%
			\path[->,font=\scriptsize]
				(A) edge node[left]{$\beta$} (A')
				(B) edge node[above]{$\mu$} (A)
				(B) edge node[right]{$U_\beta$} (B')
				(B') edge node[above]{$\mu$} (A');
		\end{tikzpicture}
		\end{equation}
\end{itemize}

@@

Here we show a sample check of a coherence law for the proof of \cref{DC}.
All relevant structure for decorated cospans is as described in \cref{thm:decorated_cospans,DC}. The coherence law that we check says that this diagram commutes:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$(M_1 \odot M_2) \otimes (N_1 \odot N_2)$};
\node (B) at (3,0) {$(N_1 \odot N_2) \otimes (M_1 \odot M_2)$};
\node (C) at (0,-.75) {$(M_1 \otimes N_1) \odot (M_2 \otimes N_2)$};
\node (D) at (3,-.75) {$(N_1 \otimes M_1) \odot (N_2 \otimes M_2)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\beta$} (B)
(B) edge node[right]{$\chi$} (D)
(A) edge node[left]{$\chi$} (C)
(C) edge node[above]{$\beta \odot \beta$} (D);
\end{tikzpicture}
\]
First of all, if we only consider the underlying cospans without their decorations, we obtain the following `flattened' commutative diagram in the symmetric monoidal double category $\lCsp(\A)$, where the top and the bottom cospans coincide:
\[
		\begin{tikzpicture}
			\node (a) at (-4,0) {$a+a'$};
			\node (b) at (1,0) {$(m_1+_b m_2) + (n_1+_{b'} n_2)$};
			\node (c) at (6,0) {$c+c'$};
			\node (a2) at (-4,1) {$a'+a$};
			\node (b2) at (1,1) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
			\node (c2) at (6,1) {$c'+c$};
            \node (a3) at (-4,2) {$a'+a$};
			\node (b3) at (1,2) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
			\node (c3) at (6,2) {$c'+c$};
            \node (a5) at (-4,-1) {$a+a'$};
			\node (b5) at (1,-1) {$(m_1+n_1) +_{(b+b')} (m_2+n_2)$};
			\node (c5) at (6,-1) {$c+c'$};
            \node (a6) at (-4,-2) {$a'+a$};
			\node (b6) at (1,-2) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
			\node (c6) at (6,-2) {$c'+c$};
			\path[->,font=\scriptsize,>=angle 90]
			(a) edge node[above]{$$} (b)
			(c) edge node[above]{$$} (b)
            (a2) edge node[above]{$$} (b2)
			(c2) edge node[above]{$$} (b2)
            (a) edge node[left]{$\beta$} (a2)
            (b) edge node[left]{$\beta$} (b2)
%(b) edge node[right]{$\tau_1$} (b2)
			(c) edge node[right]{$\beta$} (c2)
            (a3) edge node[above]{$$} (b3)
			(c3) edge node[above]{$$} (b3)
            (a2) edge node[left]{$\id$} (a3)
            (b2) edge node[left]{$\hat{\chi}$} (b3)
%(b2) edge node[right]{$\tau_2$} (b3)
			(c2) edge node[right]{$\id$} (c3)
            (a5) edge node[above]{$$} (b5)
			(c5) edge node[above]{$$} (b5)
            (a) edge node[left]{$\id$} (a5)
            (b) edge node[left]{$\hat{\chi}$} (b5)
%(b) edge node[right]{$\tau_4$} (b5)
			(c) edge node[right]{$\id$} (c5)
            (a6) edge node[above]{$$} (b6)
			(c6) edge node[above]{$$} (b6)
            (a5) edge node[left]{$\beta$} (a6)
            (b5) edge node[left]{$\beta \odot \beta$} (b6)
 %(b5) edge node[right]{$\tau_5$} (b6)
			(c5) edge node[right]{$\beta$} (c6);
		\end{tikzpicture}
	\]
where $\beta$ is the braiding of the symmetric monoidal category $\A$, $\hat{\chi}$ is the globular 2-morphism interchanging the tensor product and horizontal composition of the symmetric monoidal double category $\lCsp(\A)$, and the inwards pointing morphisms are natural maps from the each cospan's feet to its apex.

>>>>

We thank Daniel Cicala, Brendan Fong, and Joe Moeller for helpful conversations. The third author would  like  to  thank  the  General  Secretariat  for  Research  and Technology (GSRT) and the Hellenic Foundation for Research and Innovation (HFRI).

@@

Finally, the (horizontal) composition functor $\odot$ maps two composable $F$-decorated cospans $M=\left(a\to m\leftarrow b,x\in F(m)\right),N=\left(b\to n\leftarrow c,y\in F(n)\right)$ to $N\odot M$, which as a cospan is their pushout in $\A$ over their shared foot

@@

equipped with the decoration
$$y\odot x:= \one\cong\one \times \one \xrightarrow{x \times y} F(m) \times F(n) \xrightarrow{\phi_{m,n}} F(m+n) \xrightarrow{F(\psi)} F(m+_{b}n)$$

@@

their composite $\beta\odot \alpha$ is horizontal cospan composition in $\A$

@@

together with the decoration morphism $\tau_{\beta \odot \alpha} \colon F(h_1 +_g h_2)(y \odot x) \to (y' \odot x')$ given by the diagram:

@@

the isomorphism $(M_3\odot M_2)\odot M_1\cong M_3\odot (M_2\odot M_1)$ is the isomorphism of cospans 

@@

\node (E) at (5.5,0.5) {$(x_3 \odot x_2) \odot x_1 \in F((m_1+_{b} m_2)+_{c} m_3)$};
\node (F) at (5.5,-0.5) {$x_3 \odot (x_2 \odot x_1) \in F(m_1+_{b} (m_2 +_{c} m_3))$};

@@

together with an isomorphism $F(\kappa)((x_3 \odot x_2) \odot x_1) \cong (x_3 \odot (x_2 \odot x_1))$ between the decorations 

@@

\begin{thm} \label{thm:equiv}
Suppose $\A$ has finite colimits and $F \maps (\A,+) \to (\Cat,\times)$ is a symmetric lax monoidal pseudofunctor that factors through $\Rex$ as an ordinary pseudofunctor. Then the symmetric monoidal double categories $F\lCsp$ of decorated cospans and $_L\lCsp(\inta F)$ of structured cospans are isomorphic, where $L \maps \A \to \inta F$ is a left adjoint of the induced Grothendieck opfibration $U\maps \inta F \to \A$.
\end{thm}
%%% Christina: note to self, now our functor factors through that specific Rex means that each category F(a) which later becomes the fibre comes with a specific choice of colimits. We do not know what this choice is, but of course such colimits in the fibres will be isomorphic to any other we may stumble upon!

@@

Building up to an isomorphism of the above described double categories, we now define a double functor
\begin{displaymath}
\lE=(\lE_0,\lE_1)\maps _L\lCsp(\inta F) \longrightarrow F\lCsp
\end{displaymath}
which on vertical categories acts as the identity $\lE_0 = \id_{\A}$. Given a horizontal 1-cell in $_L\lCsp(\inta F)$ as in \cref{eq:scsphor1cell}, $\lE_1$ maps it to the decorated cospan $i\maps a\to m\leftarrow b:o$ with decoration $x\in F(m)$,
whereas a 2-morphism of $L$-structured cospans as in \cref{eq:2morphismLCspintaF} is mapped to the underlying map of cospans in $\A$
\begin{displaymath}
\begin{tikzcd}
a\ar[r,"i"]\ar[d,"f"'] & m\ar[d,"k"] & b\ar[l,"o"']\ar[d,"g"] \\
a'\ar[r,"i'"']& m' & b'\ar[l,"o'"]
\end{tikzcd}
\end{displaymath}
in $\A$ along with the map $\tau\maps Fk(x)\to x'$ in $F(m')$ coming from the middle arrow above, namely an $F$-decorated cospan 2-morphism. 
With these definitions, $\lE$ is indeed a double functor as in \cref{def:doublefun}: both $\lE_0$ and $\lE_1$ are functors that appropriately commute with sources and targets, and there exist globular 2-isomorphisms $\lE(N) \odot \lE(M) \simrightarrow\lE(N \odot M)$, $U_{\lE m} \simrightarrow\lE(U_m)$
for any pair of composable horizontal 1-cells $M=\cspn{(a,\bot_a)}{(m,x)}{(b,\bot_b)}{}{}$ and $N=\cspn{(b,\bot_b)}{(n,y)}{(c,\bot_c)}{}{}$ and any object $m$ of $_L\lCsp(\inta F)$. Explicitly, $\mathbb{E}(N)\odot \mathbb{E}(M)$ is given as in \cref{eq:dcospanscomposition} via the pushout cospan and decoration
\begin{equation}\label{eq:1}
 \begin{tikzcd}
  & m+_bn & \\
  a\ar[ur] && b,\ar[ul]
 \end{tikzcd}\qquad
  \one\xrightarrow{x\times y}F(m)\times F(n)\xrightarrow{\phi_{m,n}}F(m+n)\xrightarrow{F(\psi)}F(m+_bn)
\end{equation}
whereas first composing $M$ and $N$ in $_L\lCsp(\inta F)$ using pushouts in $\inta F$ as in \cref{eq:globalpushout} produces 
\begin{displaymath}
 \begin{tikzcd}[column sep={.7in,between origins}]
 && (m+_b n,F(u_m)x+_{(\bot_{m+_bn})}F(u_n)y) && \\
 & (m,x) \ar[ur] && (n,y)\ar[ul] \\
 (a,\bot_a)\ar[ur] && (b,\bot_b)\ar[ur]\ar[ul] && (c,\bot_c)\ar[ul]
 \end{tikzcd}
\end{displaymath}
where $u$ are the canonical maps into the pushout.
Under $\lE$ this is mapped to the underlying $\A$-cospan $\cspn{a}{m+_bn}{b}{}{}$ with decoration $F(u_m)x+F(u_n)y$, since a pushout over an initial object is really a coproduct. That decoration is isomorphic to that of \cref{eq:1} due to the following diagram 
\begin{equation}\label{eq:isomorphismdiag}
 \begin{tikzcd}
F(m)\times F(n)\ar[rr,"\phi"]\ar[d,"F(u_m)\times F(u_n)"']\ar[dr,phantom,"\cong"] && F(m+n)\ar[d,"F(\psi)"]\ar[d,bend right=50, phantom,"\cong"']\ar[dl,"F(u_m+u_n)"description] \\
F(m+_bn)\times F(m+_bn)\ar[r,"\phi"'] & F\left((m+_bn)+(m+_bn)\right)\ar[r,"F(\nabla)"'] & F(m+_bn)
 \end{tikzcd}
\end{equation}
where the bottom composite is the fibrewise coproduct in $F(m+_bn)$ as in \cref{eq:explicitstructure1}. The left-hand side isomorphism is due to pseudonaturality of $\phi$ whereas the right-hand side isomorphism follows from universal properties and pseudofunctoriality of $F$.
Regarding identities, the identity horizontal 1-cell $U_m$ in $_L\lCsp(\inta F)$ is $\cspn{(m,\bot_m)}{(m,\bot_m)}{(m,\bot_m)}{}{}$ with $1_m$ as the $A$-component and isomorphisms between initial objects in the fibres. Thus $\lE(U_m)$ is the identity cospan in $A$ together with the `initial decoration' $\bot_m\in F(m)$, and so is $U_{\mathbb{E}(m)}$ as in \cref{eq:UFCsp}. %Do we want to check that E is a double functor one last time?

@@

%\begin{defn}
%Let $\lD$ be a pseudo double category. Then the $\textbf{horizontal bicategory}$ of $\lD$, which we denote as $H(\lD)$, is the bicategory consisting of objects of $\lD$, morphisms that are horizontal 1-cells of $\lD$ and 2-morphisms that are globular 2-morphisms of $\lD$.
%\end{defn}
\begin{defn}\label{def:doublefun}
Given double categories $\lA$ and $\lX$, a \define{double functor} $\lF \colon\lA \to \lX$ consists of:
\begin{itemize}
\item{functors $\lF_0 \colon \lA_0 \to \lX_0$ and $\lF_1 \colon \lA_1 \to \lX_1$ such that $S \lF_1 = \lF_0 S$ and $T \lF_1 = \lF_0 T$, and}
\item{for every composable pair of horizontal 1-cells $M$ and $N$ in $\lA$, a natural transformation $\phi_{M,N} \colon \lF(N) \odot \lF(M) \to \lF(N \odot M)$ called the \define{composite comparison} and for every object $a$ in $\lA$, a natural transformation $\phi_a \colon U_{\lF_0(a)} \to \lF_1(U_a)$ called the \define{unit comparison}. The components of each of these natural transformations are globular isomorphisms which satisfy coherence axioms analogous to those of a monoidal functor.}
\end{itemize}
\end{defn}

@@

\begin{defn}
\label{defn:monoidal_double_category}
A \define{monoidal double category} is a pseudomonoid in $\Dbl$. 
\end{defn} 
\noindent
Explicitly, a monoidal double category is a double category $\lD$ with:
\begin{itemize}
\item monoidal structures on both $\lD_0$ and $\lD_1$, each with tensor product denoted $\otimes$, associator $a$, left unitor $\ell$ and right unitor $r$, such that if $I$ is the unit object of $\lD_0$ then $U_I$ is\footnote{\chris In reality, just isomorphic is OK!} the unit of $\lD_1$, and such that the source and target functors $S,T \maps \lD_1 \to \lD_0$ are strict monoidal, 
\item the structure of a double functor on $\otimes$:
that is, invertible globular 2-morphisms
\[ \chi \maps (M_2\otimes N_2)\odot(M_1\otimes N_1)  \xrightarrow{\sim}
(M_2\odot M_1)\otimes (N_2\odot N_1)\]
\[ \mu \maps U_{A\otimes B} \xrightarrow{\sim} U_A \otimes U_B\]
obeying a list of equations that can be found after \cite[Definition 2.10]{HS} and also \cite[Definition A.5]{BC}.
\end{itemize}

\begin{defn}
\label{defn:symmetric_monoidal_double_category}
A \define{symmetric monoidal double category} is a symmetric pseudomonoid in $\Dbl$. 
\end{defn}
\noindent
Explicitly, a symmetric monoidal double category is a monoidal double category $\lD$ such that:
\begin{itemize}
		\item $\lD_0$ and $\lD_1$ are symmetric monoidal categories, with braidings both denoted $\beta$.
		\item The functors $S$ and $T$ are symmetric strict monoidal functors.
		\item The following diagrams commute, expressing that the braiding is a transformation of double categories:
		\begin{equation}
		\begin{tikzpicture}\label{eq:braidingaxiom}
			\node (A) at (0,1.5) {\footnotesize{$(M_2 \odot M_1) \otimes (N_2 \odot N_1)$}};
			\node (A') at (0,0) {\footnotesize{$ (M_2\otimes N_2)\odot (M_1\otimes N_1)$}};
			\node (B) at (5,1.5) {\footnotesize{$(N_2\odot N_1) \otimes (M_2\odot M_1)$}};
			\node (B') at (5,0) {\footnotesize{$ (N_2 \otimes M_2)\odot (N_1 \otimes M_1)$}};
			%
			\path[->,font=\scriptsize]
				(A) edge node[left]{$\chi$} (A')
				(A) edge node[above]{$\beta$} (B)
				(B) edge node[right]{$\chi$} (B')
				(A') edge node[above]{$\beta \odot \beta$} (B');
		\end{tikzpicture}
		%
		\quad
		%
		\begin{tikzpicture}
			\node (A) at (0,1.5) {\footnotesize{$U_A \otimes U_B$}};
			\node (A') at (0,0) {\footnotesize{$U_B\otimes U_A$}};
			\node (B) at (2,1.5) {\footnotesize{$U_{A\otimes B} $}};
			\node (B') at (2,0) {\footnotesize{$U_{B\otimes A}$}};
			%
			\path[->,font=\scriptsize]
				(A) edge node[left]{$\beta$} (A')
				(B) edge node[above]{$\mu$} (A)
				(B) edge node[right]{$U_\beta$} (B')
				(B') edge node[above]{$\mu$} (A');
		\end{tikzpicture}
		\end{equation}
\end{itemize}

@@

Here we show a sample check of a coherence law for the proof of \cref{DC}.
All relevant structure for decorated cospans is as described in \cref{thm:decorated_cospans,DC}. The coherence law that we check says that this diagram commutes:
\[
\begin{tikzpicture}[scale=1.5]
\node (A) at (0,0) {$(M_2 \odot M_1) \otimes (N_2 \odot N_1)$};
\node (B) at (3,0) {$(N_2 \odot N_1) \otimes (M_2 \odot M_1)$};
\node (C) at (0,-.75) {$(M_2 \otimes N_2) \odot (M_1 \otimes N_1)$};
\node (D) at (3,-.75) {$(N_2 \otimes M_2) \odot (N_1 \otimes M_1)$};
\path[->,font=\scriptsize,>=angle 90]
(A) edge node[above]{$\beta$} (B)
(B) edge node[right]{$\chi$} (D)
(A) edge node[left]{$\chi$} (C)
(C) edge node[above]{$\beta \odot \beta$} (D);
\end{tikzpicture}
\]
{\chris Chai's in the definition of a monoidal double category have a different direction. Since it is an isomorphism it doesn't really change anything, but consider changing to keep them right}
First of all, if we only consider the underlying cospans without their decorations, we obtain the following `flattened' commutative diagram in the symmetric monoidal double category $\lCsp(\A)$, where the top and the bottom cospans coincide:
\[
		\begin{tikzpicture}
			\node (a) at (-4,0) {$a+a'$};
			\node (b) at (1,0) {$(m_1+_b m_2) + (n_1+_{b'} n_2)$};
			\node (c) at (6,0) {$c+c'$};
			\node (a2) at (-4,1) {$a'+a$};
			\node (b2) at (1,1) {$(n_1 +_{b'} n_2) + (m_1 +_b m_2)$};
			\node (c2) at (6,1) {$c'+c$};
            \node (a3) at (-4,2) {$a'+a$};
			\node (b3) at (1,2) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
			\node (c3) at (6,2) {$c'+c$};
            \node (a5) at (-4,-1) {$a+a'$};
			\node (b5) at (1,-1) {$(m_1+n_1) +_{(b+b')} (m_2+n_2)$};
			\node (c5) at (6,-1) {$c+c'$};
            \node (a6) at (-4,-2) {$a'+a$};
			\node (b6) at (1,-2) {$(n_1+m_1) +_{(b'+b)} (n_2+m_2)$};
			\node (c6) at (6,-2) {$c'+c$};
			\path[->,font=\scriptsize,>=angle 90]
			(a) edge node[above]{$$} (b)
			(c) edge node[above]{$$} (b)
            (a2) edge node[above]{$$} (b2)
			(c2) edge node[above]{$$} (b2)
            (a) edge node[left]{$\beta$} (a2)
            (b) edge node[left]{$\beta$} (b2)
%(b) edge node[right]{$\tau_1$} (b2)
			(c) edge node[right]{$\beta$} (c2)
            (a3) edge node[above]{$$} (b3)
			(c3) edge node[above]{$$} (b3)
            (a2) edge node[left]{$\id$} (a3)
            (b2) edge node[left]{$\hat{\chi}$} (b3)
%(b2) edge node[right]{$\tau_2$} (b3)
			(c2) edge node[right]{$\id$} (c3)
            (a5) edge node[above]{$$} (b5)
			(c5) edge node[above]{$$} (b5)
            (a) edge node[left]{$\id$} (a5)
            (b) edge node[left]{$\hat{\chi}$} (b5)
%(b) edge node[right]{$\tau_4$} (b5)
			(c) edge node[right]{$\id$} (c5)
            (a6) edge node[above]{$$} (b6)
			(c6) edge node[above]{$$} (b6)
            (a5) edge node[left]{$\beta$} (a6)
            (b5) edge node[left]{$\beta \odot \beta$} (b6)
 %(b5) edge node[right]{$\tau_5$} (b6)
			(c5) edge node[right]{$\beta$} (c6);
		\end{tikzpicture}
	\]
where $\beta$ is the braiding of the symmetric monoidal category $\A$, $\hat{\chi}$ is the globular 2-morphism interchanging the tensor product and horizontal composition of the symmetric monoidal double category $\lCsp(\A)$, and the inwards pointing morphisms are natural maps from the each cospan's feet to its apex.
